Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-08-16 doc/manuscript/manuscript.Rmd
I have added a by-year component.
I realized that I never analyzed the data across
years, which I should have done from the beginning.

This brought us a new AMOVA table that makes more
sense and some new questions regarding WA in 2008.

After collection, the isolates were stored in petri plates lined with filter paper, then stored at $20^{\circ}$F or –$4^{\circ}$C. 
Sclerotia were triple rinsed with (i) 50% Clorox bleach/50% double-distilled (dd)H2O solution for 3 min, (ii) ddH2O rinse for 3 min, and (iii) final ddH2O rinse for 3 min, then plated on water agar plates (16g of Bacto agar per liter of ddH2O), with four to five sclerotia of each isolate separated on each plate and stored on the bench top at room temperature for 5 to 6 days An 8-mm plug from a 5- or 6-day-old culture was transferred from the advancing margin of the mycelia onto a plate of Difco potato dextrose agar (PDA at 39 g/liter of ddH2O) [@otto-hanson2011variation].
In combination with the 156 isolates described previously, we collected 210 isolates for a total of 366 isolates [@otto-hanson2011variation].

@@

```{r table4, echo = FALSE, warning = FALSE, message = FALSE, results = "asis"}
suppressPackageStartupMessages(library("tidyverse"))
read_csv("../../results/tables/AMOVA-region.csv", 
         na = "NA", # spaces read in as spaces
         col_types = cols(.default = col_character()))  %>%
  rename(ps = `Phi statistic`) %>%
  mutate(ps = gsub("0\\.00(\\d{1})(\\d{2})", "\\1.\\2e^-3^", ps)) %>%
  mutate(ps = case_when(Hierarchy == "Between Source" ~ ps, TRUE ~ paste0("**", ps, "**"))) %>%
  rename(`$\\Phi statistic$` = ps) %>%
  rename(`% variation` = `Percent variation`) %>%
  rename(S.S. = `Sum of Squares`) %>%
  select(-P) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>% 
  huxtable::set_col_width(c(1.1, 0.6, 0.9, 0.9, 1.4)) %>% 
  huxtable::set_align(huxtable::everywhere, 2:5, "center") %>% 
  huxtable::print_md(max_width = 100)
```

Table: (\#tab:amova) Analysis of Molecular Variance on Bruvo's genetic distance showing little differentiation between white mold screening nurseries (wmn) and other sources. The hierarchy was constructed as Source/Region where source is defined as belonging to a wmn or not. Bold $\Phi$ values indicate significant values (P < 1.00e^-4^). Numbers in parentheses represent AMOVA run with the regions NE, WA, and MI. S.S. = Sum of Squares, d.f. = degrees of freedom.

>>>>

After collection, the isolates were stored in petri plates lined with filter paper, then stored at $20^{\circ}$F or -$4^{\circ}$C. 
Sclerotia were triple rinsed with (i) 50% Clorox bleach/50% double-distilled (dd)H2O solution for 3 min, (ii) ddH2O rinse for 3 min, and (iii) final ddH2O rinse for 3 min, then plated on water agar plates (16g of Bacto agar per liter of ddH2O), with four to five sclerotia of each isolate separated on each plate and stored on the bench top at room temperature for 5 to 6 days An 8-mm plug from a 5- or 6-day-old culture was transferred from the advancing margin of the mycelia onto a plate of Difco potato dextrose agar (PDA at 39 g/liter of ddH2O) [@otto-hanson2011variation].
In combination with the 156 isolates described previously, we collected 210 isolates for a total of 366 isolates [@otto-hanson2011variation].

@@

```{r table4, echo = FALSE, warning = FALSE, message = FALSE, results = "asis"}
suppressPackageStartupMessages(library("tidyverse"))
read_csv("../../results/tables/AMOVA-year.csv", 
         na = "NA", # spaces read in as spaces
         col_types = cols(.default = col_character()))  %>%
  rename(ps = `Phi statistic`) %>%
  # mutate_if(is.numeric, format, digits = 3) %>%
  mutate(ps = signif(as.numeric(ps), digits = 3)) %>%
  mutate(ps = gsub("0\\.00(\\d{1})(\\d{2})", "\\1.\\2e^-3^", ps)) %>%
  mutate(ps = case_when(P > 0.05 ~ ps, TRUE ~ paste0("**", ps, "**"))) %>%
  rename(`$\\Phi$ statistic` = ps) %>%
  rename(`% variation` = `Percent variation`) %>%
  rename(S.S. = `Sum of Squares`) %>%
  rename(`*P*` = P) %>%
  select(c(1:4, 6, 5)) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>% 
  huxtable::set_col_width(c(0.8, 0.15, 0.15, 0.35, 0.5, 0.15)) %>% 
  huxtable::set_align(huxtable::everywhere, 2:6, "right") %>% 
  huxtable::set_number_format(huxtable::everywhere, 2, 0) %>%
  huxtable::set_number_format(huxtable::everywhere, 6, 3) %>%
  huxtable::set_number_format(huxtable::everywhere, 5, 4) %>%
  huxtable::print_md(max_width = 80)
```

Table: (\#tab:amova) Analysis of Molecular Variance on Bruvo's genetic distance showing little differentiation between white mold screening nurseries (wmn) and other sources. The hierarchy was constructed as Source/Region where source is defined as belonging to a wmn or not. Bold $\Phi$ values indicate significant values (*P* < 0.05). S.S. = Sum of Squares, d.f. = degrees of freedom.
